Inequalities by ethnicity in the CHD pathway

### 2024-03-07 findings.qmd
Add functions to create IoD calcs and plots by region and ICB

---
title: "Inequalities by ethnicity in the CHD pathway"
lang: en-GB
author: "Jacqueline Grout"
date: last-modified
date-format: "YYYY-MM-DD"
format:
  html:
    grid:
      sidebar-width: 250px
      body-width: 800px
      margin-width: 250px
      gutter-width: 1.5rem
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Contents
    toc-depth: 3
editor: visual
execute:
  echo: false
  message: false
  warning: false
  freeze: auto
editor_options: 
  chunk_output_type: console
---

@@

library(tidyverse)
```

@@

```{r}
tar_read(rel_iod_chart)
```

@@

@@

>>>>

---
title: "Inequalities by ethnicity in the CHD pathway"
lang: en-GB
author: "Jacqueline Grout"
date: last-modified
date-format: "YYYY-MM-DD"
format:
  html:
    grid:
      sidebar-width: 200px
      body-width: 950px
      margin-width: 150px
      gutter-width: 1.5rem
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Contents
    toc-depth: 3
editor: visual
execute:
  echo: false
  message: false
  warning: false
  freeze: auto
editor_options: 
  chunk_output_type: console
---

@@

library(tidyverse)
library(grid)
library(gridExtra)
library(cowplot)
```

@@

@@

## Regions - Relative Index of Disparity

### London

```{r}
regional_charts <- tar_read(regional_charts)
regional_charts[1]
```

### South West

```{r}

regional_charts[2]
```

### South East

```{r}

regional_charts[3]
```

### Midlands

```{r}
regional_charts[4]
```

### East of England

```{r}
regional_charts[5]
```

### North West

```{r}
regional_charts[6]
```

### North East and Yorkshire

```{r}
regional_charts[7]
```

```{r}

@@

### ICBs- Relative Index of Disparity

```{r}
icb_charts <- tar_read(icb_charts)
icb_charts[1]
icb_charts[2]
icb_charts[3]
icb_charts[4]
icb_charts[5]
icb_charts[6]
icb_charts[7]
icb_charts[8]
icb_charts[9]
icb_charts[10]
icb_charts[11]
icb_charts[12]
```
